Detailed Chemical Abundances with \tc

### 2015-08-28 article/ms.tex
Good enough for government work

% Convenient maths.
\newcommand\K{$\mathbf{K}$}
\newcommand\lv{\bf{\boldsymbol\ell_n}}
\newcommand\cv{{\boldsymbol\theta}_\lambda}
\newcommand\given{|}

@@

This form is flexible: the label vector $\lv$ may be linear in just a few labels
or a complex combination of all $K$ available labels. The underlying principle
is that the flux for any pixel from any star is predictable with a very simple
model (generally a polynomial), given the labels. Indeed, \citet{Ness2015}
employ a quadratic-in-labels (see their Equation 8) spectral model using stellar
parameters (effective temperature $T_{\rm eff}$, surface gravity $\log{g}$, and 
metallicity [M/H]\footnote{\citet{Ness2015} use [Fe/H] in $\lv$, but for the 
sake of distinguishing between overall metallicity and individual abundances,
we opt for [M/H] to describe overall metallicity throughout this \article{}})
and demonstrate by cross-validation that these labels can be 
measured with a precision of 95~K in $T_{\rm eff}$, 0.24 in $\log{g}$, 0.08 in 
[M/H], with negligible biases. It is important to note that these uncertainties
are comparable to those reported by \textit{curve-of-growth} techniques, which
rely on a model atmosphere and the changing strength of atomic absorption lines.

@@

>>>>

% Convenient maths.
\newcommand\K{$\mathbf{K}$}
\newcommand\lv{\mathbf{\boldsymbol\ell_n}}
\newcommand\cv{{\boldsymbol\theta}_\lambda}
\newcommand\given{|}

@@

This form is flexible: the label vector $\lv$ may be linear in just a few labels
or a complex combination of all $K$ available labels. The underlying principle
is that the flux for any pixel from any star is predictable with a very simple
model (generally a polynomial), given the labels. Indeed, \citet{Ness2015}
employ a quadratic-in-labels (see their Equation 8) spectral model using stellar
parameters (effective temperature $T_{\rm eff}$, surface gravity $\log{g}$, and 
metallicity [M/H]\footnote{\citet{Ness2015} use [Fe/H] in $\lv$, but for the 
sake of distinguishing between overall metallicity and individual abundances,
we opt for [M/H] to describe overall metallicity throughout this \article{}})
and demonstrate by cross-validation that these labels can be 
measured with a precision of 95~K in $T_{\rm eff}$, 0.24 in $\log{g}$, 0.08 in 
[M/H], with negligible biases. It is important to note that these uncertainties
are comparable to those reported from using \textit{curve-of-growth} on similar 
data sets (e.g., \citet{X,Y}).

@@

Before extending this framework to include individual chemical abundances, it is
a useful exercise to understand \textit{why} a simple polynomial model can 
approximate spectral synthesis calculations with comparable fidelity. The reason
extends past model flexibility: one could imagine a similar coefficient vector
$\cv$ with a different functional form of the label vector $\lv$ (e.g., an
extreme case might be $\lv \equiv [1, {\rm [M/H]}^{T_{\rm eff}},
\log{g}^{T_{\rm eff}}]$) which would probably be incapable of describing
spectral fluxes with any fidelity.

% Describe the model of EW formation

% How this changes as a function of teff, logg, feh

% dealing with integrated EW.
% APOGEE is R ~ 20,000
